## Homework 3

<!--
You can use the example3.Rmd or other files to find examples
of the codes you'll need to use to complete this assignment. I strongly
urge you to copy and paste relevant code that you know works from my
examples or instructions and then edit that code so you're working
with the appropriate variables for the homework.
-->

<!--
Set the working directory.
No Rchunk is needed to accomplish this.
-->

<!--
Read in the homework3.csv data. For each of the following steps you
should preface your R commands with some plain English explanation.
-->
#### Code to read the data in homework 3

```{r}
dat<-read.csv("homework3.csv")
```

<!--
Check the structure of the data.
-->

#### Code to check structure of data in homework 3

```{r}
str(dat)
```

<!--
Find the mean, median, and standard deviation using the sd() function
for the overall level of conservatism.
-->
#### The code for finding the mean, median, and sd is the following. 

```{r}
mean(dat$conservatism)
median(dat$conservatism)
sd(dat$conservatism)
```

**The mean for conservatism is 52.29
The median for conservatism is 53.83
The standard deviation for conservatism is 19.76**

<!--
Find the mean level of support for freshmen only.
-->

####The code for finding the mean level of support for freshman students

```{r}
mean(dat$conservatism[dat$year=="freshman"])
```
**The mean level of support for freshman is 47.5**

<!--
Find the mean level of support for male business students only.
-->

####The code for mean for sophomore students in business.

```{r}
mean(dat$conservatism[dat$year=="sophomore" & dat$major=="business"])
```
**The mean for sophomore students in business is 61.6**