## Homework 4

<!--
Remember you can use the example4.Rmd or other files to find examples
of the codes you'll need to use to complete this assignment. I strongly
urge you to copy and paste relevant code that you know works from my
examples or instructions and then edit that code so you're working
with the appropriate variables for the homework.
-->

<!--
Set the working directory.
No Rchunk is needed to accomplish this.
-->

<!--
Read in the homework4.csv data. For each of the following steps you
should preface your R commands with some plain English explanation.
-->
####The first code is used to read in the data.
```{r}
dat<-read.csv("example4.csv")
```


<!--
Check the structure of the data.
-->
####The following code checks the structure. 
```{r}
str(dat)
```
####The data frame shows two levels; major (engineering and psychology) and gender (female and male).

<!--
Create a table that shows how many people fell into each category.
-->
####The following code creates a table showing the number of people in each category. 
```{r}
table(dat$major, dat$gender)
```
####The table shows that in engineering there are 11 females and 19 males and in psychology there are 18 females and 12 males.

<!--
Perform a chi-square test to determine whether or not the experimental
conditions and agreement with a statement are independent or related.
Also, interpret the results of your test and provide a a statistical
statement that supports your interpretation. As there's no way to
insert the chi-square symbol, you can just use chi-square instead
(see example4.Rmd).
-->
####The following code is used to run a chi-square test to analyze the data.
```{r}
chisq.test(dat$major,dat$gender)
```
####The test shows that major and gender are unrelated.
Chi-square = 2.4, p = .12
